---
title: "Results"
output:
  html_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library("psych", lib.loc = "~/R/win-library/3.3")
library("zoom", lib.loc = "~/R/win-library/3.3")
library("knitr", lib.loc = "~/R/win-library/3.3")
```

```{r load data, echo=FALSE, message=FALSE, warning=FALSE}
Statistics <-
  read.csv(
    file = "Parameters.csv",
    header = TRUE,
    sep = ",",
    quote = "\"",
    dec = "."
  )
stat <- Statistics[, -40:-69]
stat <- stat[, -2]

stat <- stat[stat$problem != "HydraulicLeaking",]
stat <- stat[stat$problem != "HydraulicPlanning",]

mininst <- 7
numinst <- 0
probs <- c()
for (pro in unique(stat[, 1])) {
  st <- stat[stat$problem == pro, ]
  lenst <- sum(!is.na(st[, 1]))
  if (lenst >= mininst) {
    numinst <- numinst + 1
    probs <- c(probs, pro)
  }
}

probs <- probs[order(probs)]
timesLow <- matrix(nrow = numinst, ncol = 2)
timesHigh <- matrix(nrow = numinst, ncol = 2)
timesNA <- matrix(nrow = numinst, ncol = 2)
i <- 1
for (pro in unique(stat[, 1])) {
  st <- stat[stat$problem == pro, ]
  lenst <- sum(!is.na(st[, 1]))
  if (lenst >= mininst) {
    timesLow[i, 1] <- pro
    timesLow[i, 2] <- 0
    timesHigh[i, 1] <- pro
    timesHigh[i, 2] <- 0
    timesNA[i, 1] <- pro
    timesNA[i, 2] <- 0
    i <- i + 1
  }
}

numCorrelations <- 0

paramHighLow <- matrix(nrow = 40, ncol = 3)
```

```{r printAll, echo=FALSE, message=FALSE, warning=FALSE}
printAll <- function(param, problems, labelx) {
  for (pro in probs) {
    st <- stat[stat$problem == pro,]
    
    File <- paste("./Plots/", labelx, "/", pro, ".png", sep = "")
    dir.create(dirname(File), showWarnings = FALSE)
    
    png(file = File, bg = "white", res = 144)
    plot(
      x = combineParams(param, st),
      y = st$CPU_time,
      xlab = labelx,
      ylab = "CPU_time",
      pch = "+",
      main = pro
    )
    dev.off()
    
    cat(sprintf("\n\n###Problem: %s\n\n", pro))
    plot(
      x = combineParams(param, st),
      y = st$CPU_time,
      xlab = labelx,
      ylab = "CPU_time",
      pch = "+",
      main = pro
    )
  }
  
}

```

```{r printTable, echo=FALSE, message=FALSE, warning=FALSE}
printTable <- function(mytable, label) {
  tableOrdered <-
    mytable[order(as.numeric(mytable[, 2]), decreasing = TRUE), ]
  lines <- c(
    "\\begin{table}[H]",
    "  \\centering",
    "  \\small",
    "  \\begin{tabular}{ll}",
    "    \\toprule",
    paste(
      "    \\textbf{Benchmark set}      & \\textbf{Times ",
      label,
      "}\\\\",
      sep = ""
    ),
    "    \\midrule"
  )
  
  for (a in 1:nrow(tableOrdered)) {
    lines <- c(lines,
               paste("    ",
                     tableOrdered[a, 1],
                     " & ",
                     tableOrdered[a, 2],
                     "\\\\",
                     sep = ""))
  }
  
  lines <- c(
    lines,
    "    \\bottomrule",
    "  \\end{tabular}",
    paste(
      "  \\caption[Table number ",
      label,
      " correlations]{Times a Set was in a ",
      label,
      " correlation}",
      sep = ""
    ),
    paste("  \\label{table-correlations-", label, "}", sep = ""),
    "\\end{table}"
  )
  File <- file(paste("./Plots/", label, "Table.tex", sep = ""))
  writeLines(lines, File)
  close(File)
}
```

```{r printTableHighLow, echo=FALSE, message=FALSE, warning=FALSE}
printTableHighLow <- function() {
  tableOrdered <-
    paramHighLow[order(as.numeric(paramHighLow[, 2]), decreasing = TRUE),]
  lines <- c(
    "\\small ",
    "\\begin{longtable}{p{0.8\\textwidth}ll}",
    "  \\toprule",
    "  \\textbf{Parameter}      & \\textbf{High}      & \\textbf{Low}\\\\",
    "  \\midrule"
  )
  
  for (a in 1:nrow(tableOrdered)) {
    lines <- c(lines,
               paste("  ",
                     tableOrdered[a, 1],
                     " & ",
                     tableOrdered[a, 2],
                     " & ",
                     tableOrdered[a, 3],
                     "\\\\",
                     sep = ""))
  }
  
  lines <- c(
    lines,
    "  \\bottomrule",
    "  \\caption[Table High Low corr.]{Number of High and low correlations per parameter. Parameters marked with a * are for k-consistency and parameters marked with \\# are for hardness parameters from \\mbox{Fichte et. al. \\cite{TR/FichteKroneggerWoltran16}}.}",
    "  \\label{table-highlow-correlations}",
    "\\end{longtable}"
  )
  File <- file("./Plots/HighLowTable.tex")
  writeLines(lines, File)
  close(File)
}
```

```{r printLatexTable, echo=FALSE, message=FALSE, warning=FALSE}
printLatexTable <- function(correlations, param, label, prefix="") {
  highcorrelations <- list()
  lowcorrelations <- list()
  high <- 1
  low <- 1
  problems <- c()
  lines <- c()
  
  for (a in 1:nrow(correlations)) {
    if (!is.na(correlations[a, 2])) {
      if (abs(as.numeric(correlations[a, 2])) >= 0.7) {
        highcorrelations[[high]] <-
          c(correlations[a, 1], correlations[a, 2])
        problems <- c(problems, correlations[a, 1])
        timesHigh[timesHigh[, 1] == correlations[a, 1], 2] <<-
          as.numeric(timesHigh[timesHigh[, 1] == correlations[a, 1], 2]) + 1
        high <- (high + 1)
      }
      if (abs(as.numeric(correlations[a, 2])) <= 0.2) {
        lowcorrelations[[low]] <- c(correlations[a, 1], correlations[a, 2])
        problems <- c(problems, correlations[a, 1])
        timesLow[timesLow[, 1] == correlations[a, 1], 2] <<-
          as.numeric(timesLow[timesLow[, 1] == correlations[a, 1], 2]) + 1
        low <- (low + 1)
      }
    } else{
      lowcorrelations[[low]] <- c(correlations[a, 1], correlations[a, 2])
      problems <- c(problems, correlations[a, 1])
      timesNA[timesNA[, 1] == correlations[a, 1], 2] <<-
        as.numeric(timesNA[timesNA[, 1] == correlations[a, 1], 2]) + 1
      low <- (low + 1)
    }
  }
  
  high <- high - 1
  low <- low - 1
  paramHighLow[numCorrelations,1] <<- paste(prefix,label,sep=" ")
  paramHighLow[numCorrelations,2] <<- high
  paramHighLow[numCorrelations,3] <<- low
  
  lines <- c(
    lines,
    "",
    "\\begin{table}[H]",
    "  \\centering",
    "  \\small",
    "  \\begin{tabular}{ll|ll}",
    "    \\toprule",
    "    \\textbf{Benchmark set}              & \\textbf{Corr}     & \\textbf{Benchmark set}    & \\textbf{Corr}\\\\",
    "    \\midrule"
  )
  
  for (a in seq(1,(high+low),2)) {
    if ((a+1) <= high) {
      lines <- c(
        lines,
        paste(
          "    ",
          highcorrelations[[a]][1],
          " & ",
          highcorrelations[[a]][2],
          " & ",
          highcorrelations[[a+1]][1],
          " & ",
          highcorrelations[[a+1]][2],
          "\\\\",
          sep = ""
        )
      )
      
    } else if ((a == high)&((a+1) <= (high+low))) {
      lines <- c(
        lines,
        paste(
          "    ",
          highcorrelations[[a]][1],
          " & ",
          highcorrelations[[a]][2],
          " & ",
          lowcorrelations[[a+1-high]][1],
          " & ",
          lowcorrelations[[a+1-high]][2],
          "\\\\",
          sep = ""
        )
      )
      
    } else if ((a+1)<=(high+low)) {
      lines <- c(
        lines,
        paste(
          "    ",
          lowcorrelations[[a-high]][1],
          " & ",
          lowcorrelations[[a-high]][2],
          " & ",
          lowcorrelations[[a+1-high]][1],
          " & ",
          lowcorrelations[[a+1-high]][2],
          "\\\\",
          sep = ""
        )
      )
      
    } else if((a)==(high)){
      lines <- c(
        lines,
        paste(
          "    ",
          highcorrelations[[a]][1],
          " & ",
          highcorrelations[[a]][2],
          " & ",
          " & ",
          "\\\\",
          sep = ""
        )
      )
    } else if(((a)==(high+low))&(low>0)){
      lines <- c(
        lines,
        paste(
          "    ",
          lowcorrelations[[a-high]][1],
          " & ",
          lowcorrelations[[a-high]][2],
          " & ",
          " & ",
          "\\\\",
          sep = ""
        )
      )
    }
  }
  
  lines <- c(
    lines,
    "    \\bottomrule",
    "  \\end{tabular}",
    paste(
      "  \\caption[Table corr. ",
      label,
      "]{Spearman Correlation between time and ",
      label,
      ". The mean of the correlations is ",round(mean(as.numeric(correlations[,2]),na.rm = TRUE),digits=2),
      ". The standard deviation of the correlations is ",round(sd(abs(as.numeric(correlations[,2])),na.rm = TRUE),digits=2),
      ".}",
      sep = ""
    ),
    paste("  \\label{table-correlations-",
          label,
          "}",
          sep = ""),
    "\\end{table}"
  )
  File <- file(paste("./Plots/", label, ".tex", sep = ""))
  writeLines(lines, File)
  close(File)
  printAll(param, problems, label)
}

```

```{r combineParams, echo=FALSE, message=FALSE, warning=FALSE}
combineParams <- function(params, st) {
  combined <- st[, params[1]]
  params <- params[-1]
  for (a in params) {
    combined <- combined + st[, a]
  }
  return(combined)
}
```

```{r genCors, echo=FALSE, message=FALSE, warning=FALSE}
genCors <- function(param, label, algo, prefix="") {
  numCorrelations <<- numCorrelations + 1
  num <- 1
  cormatrix_stat <- matrix(ncol = 2, nrow = numinst)
  
  for (pro in unique(stat[, 1])) {
    st <- stat[stat$problem == pro,]
    lenst <- sum(!is.na(st[, 1]))
    if (lenst >= mininst) {
      cormatrix_stat[num, 1] <- pro
      a <-
        cor.test(as.numeric(combineParams(param, st)), as.numeric(st$CPU_time), method = algo)
      cormatrix_stat[num, 2] <- round(a$estimate, digits = 2)
      num <- num + 1
    }
  }
  asdf <-
    cor.test(combineParams(param, stat), stat$CPU_time, method = algo)
  cat(sprintf("\nOverall Correlation: %f\n\n",round(a$estimate, digits = 2)))
  correlations <-
    cormatrix_stat[order(cormatrix_stat[, 2], decreasing = TRUE), ]
  print(kable(correlations, col.names = c("Problems", "Correlation")))
  printLatexTable(correlations, param, label, prefix)
}
```

# one parameter combinations
## numChoices
```{r spearman numChoices, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numChoices"),"numChoices","spearman")
```

## numConflicts
```{r spearman numConflicts, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numConflicts"),"numConflicts","spearman")
```

## numRestarts
```{r spearman numRestarts, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numRestarts"),"numRestarts","spearman")
```

## numAtoms
```{r spearman numAtoms, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numAtoms"),"numAtoms","spearman")
```

## numBodies
```{r spearman numBodies, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numBodies"),"numBodies","spearman")
```

## numVariables
```{r spearman numVariables, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numVariables"),"numVariables","spearman")
```

## numConstraints
```{r spearman numConstraints, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numConstraints"),"numConstraints","spearman")
```

## numNonDualHornClauses
```{r spearman numNonDualHornClauses, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numNonDualHornClauses"),"numNonDualHornClauses","spearman")
```

## numVPosLit
```{r spearman numVPosLit, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numVPosLit"),"numVPosLit","spearman")
```

## numAtomOccC
```{r spearman numAtomOccC, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numAtomOccC"),"numAtomOccC","spearman")
```

## numAtomsPosBody
```{r spearman numAtomsPosBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numAtomsPosBody"),"numAtomsPosBody","spearman")
```

# two parameter combinations
## numAtoms + numChoices
```{r spearman numAtoms + numChoices, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numAtoms" , "numChoices"),"numAtoms + numChoices","spearman")
```

## numAtoms + numConflicts
```{r spearman numAtoms + numConflicts, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(4,9),"numAtoms + numConflicts","spearman")
```

## numNonHornClauses + numVariables
```{r spearman numNonHornClauses + numVariables, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(17,13),"numNonHornClauses + numVariables","spearman")
```

## maxNumAtomOcc + numEquivalences
```{r spearman maxNumAtomOcc + numEquivalences, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxNumAtomOcc" , "numEquivalences"),"maxNumAtomOcc + numEquivalences","spearman")
```

## numAtomsNegBody + numVariables
```{r spearman numAtomsNegBody + numVariables, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(49,13),"numAtomsNegBody + numVariables","spearman")
```

## maxSizeAnswerSet + numNonHornClauses
```{r spearman maxSizeAnswerSet + numNonHornClauses, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52,17),"maxSizeAnswerSet + numNonHornClauses","spearman")
```

## maxSizeAnswerSet + numAtomsNegBody
```{r spearman maxSizeAnswerSet + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52,49),"maxSizeAnswerSet + numAtomsNegBody","spearman")
```

# three parameter combinations
## numVNegLitH + numNonDualHornClauses + numAtoms
```{r spearman numVNegLitH + numNonDualHornClauses + numAtoms, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numVNegLitH" , "numNonDualHornClauses" , "numAtoms"),"numVNegLitH + numNonDualHornClauses + numAtoms","spearman")
```

## numVNegLitH + numNonDualHornClauses + numVariables
```{r spearman numVNegLitH + numNonDualHornClauses + numVariables, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numVNegLitH" , "numNonDualHornClauses" , "numVariables"),"numVNegLitH + numNonDualHornClauses + numVariables","spearman")
```

## numVNegLitH + numVPosLit + numNonDualHornClauses
```{r spearman numVNegLitH + numVPosLit + numNonDualHornClauses, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("numVNegLitH" , "numVPosLit" , "numNonDualHornClauses"),"numVNegLitH + numVPosLit + numNonDualHornClauses","spearman")
```

# k Consistency
## numAtomsHead
```{r spearman numAtomsHead, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(47),"numAtomsHead","spearman","*")
```

## maxSizeRuleHead + numRules
```{r spearman maxSizeRuleHead + numRules, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(42,10),"maxSizeRuleHead + numRules","spearman","*")
```

## maxSizeAnswerSet + maxSizeHeadNegBodyRule
```{r spearman maxSizeAnswerSet + maxSizeHeadNegBodyRule, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52,41),"maxSizeAnswerSet + maxSizeHeadNegBodyRule","spearman","*")
```

## numNonHornClauses + maxSizeHeadNegBodyRule
```{r spearman numNonHornClauses + maxSizeHeadNegBodyRule, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(17,41),"numNonHornClauses + maxSizeHeadNegBodyRule","spearman","*")
```

## maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + maxSizeNegBodyCon + numAtomsNegBody
```{r spearman maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + maxSizeNegBodyCon + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52,48,51,46,49),"maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + maxSizeNegBodyCon + numAtomsNegBody","spearman","*")
```

## numAtomsPosBody + numNonHornClauses + maxSizeNegBodyCon + numAtomsNegBody
```{r spearman numAtomsPosBody + numNonHornClauses + maxSizeNegBodyCon + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(48,17,46,49),"numAtomsPosBody + numNonHornClauses + maxSizeNegBodyCon + numAtomsNegBody","spearman","*")
```

## maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + numRules + numAtomsNegBody
```{r spearman maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + numRules + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52,48,51,10,49),"maxSizeAnswerSet + numAtomsPosBody + maxNumVarOccHeadNegBody + numRules + numAtomsNegBody","spearman","*")
```

## numAtomsPosBody + numNonHornClauses + numRules + numAtomsNegBody
```{r spearman numAtomsPosBody + numNonHornClauses + numRules + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(48,17,10,49),"numAtomsPosBody + numNonHornClauses + numRules + numAtomsNegBody","spearman","*")
```

## numRules + numAtomsNegBody
```{r spearman numRules + numAtomsNegBody, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(10,49),"numRules + numAtomsNegBody","spearman","*")
```

## maxSizeHeadNegBodyRule + numNonHornClauses
```{r spearman maxSizeHeadNegBodyRule + numNonHornClauses, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(41,17),"maxSizeHeadNegBodyRule + numNonHornClauses","spearman","*")
```

## numRules
```{r spearman numRules, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(10),"numRules","spearman","*")
```

## maxSizeAnswerSet
```{r spearman maxSizeAnswerSet, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c(52),"maxSizeAnswerSet","spearman","*")
```

# Hardness
## maxSizeNCon + maxNumAtomOcc + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC
```{r spearman maxSizeNCon + maxNumAtomOcc + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeNCon", "maxNumAtomOcc", "numAtomsPosBody", "numConstraints", "maxSizeNegBodyCon", "numAtomOccC"),"maxSizeNCon + maxNumAtomOcc + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC","spearman","\\#")
```

## maxSizeAnswerSet + maxSizeNegBodyRule + maxSizePosBodyCon + maxSizeNegBodyCon
```{r spearman maxSizeAnswerSet + maxSizeNegBodyRule + maxSizePosBodyCon + maxSizeNegBodyCon, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeAnswerSet", "maxSizeNegBodyRule", "maxSizePosBodyCon", "maxSizeNegBodyCon"),"maxSizeAnswerSet + maxSizeNegBodyRule + maxSizePosBodyCon + maxSizeNegBodyCon","spearman","\\#")
```

## maxSizeAnswerSet + maxSizePosBodyNCon + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC
```{r spearman maxSizeAnswerSet + maxSizePosBodyNCon + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeAnswerSet", "maxSizePosBodyNCon", "numAtomsPosBody", "numConstraints", "maxSizeNegBodyCon", "numAtomOccC"),"maxSizeAnswerSet + maxSizePosBodyNCon + numAtomsPosBody + numConstraints + maxSizeNegBodyCon + numAtomOccC","spearman","\\#")
```

## maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numAtomsPosBody + numRules
```{r spearman maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numAtomsPosBody + numRules, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeAnswerSet", "maxSizePosBodyNCon", "numNonHornClauses", "maxNumAtomOcc", "numAtomsPosBody", "numRules"),"maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numAtomsPosBody + numRules","spearman","\\#")
```

## maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumVarOccHeadNegBody + numConstraints + maxSizeNegBodyCon + numAtomOccC
```{r spearman maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumVarOccHeadNegBody + numConstraints + maxSizeNegBodyCon + numAtomOccC, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeAnswerSet", "maxSizePosBodyNCon", "numNonHornClauses", "maxNumVarOccHeadNegBody", "numConstraints", "maxSizeNegBodyCon", "numAtomOccC"),"maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumVarOccHeadNegBody + numConstraints + maxSizeNegBodyCon + numAtomOccC","spearman","\\#")
```

## maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numConstraints + maxSizeNegBodyCon + numAtomOccC
```{r spearman maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numConstraints + maxSizeNegBodyCon + numAtomOccC, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizePosBodyNCon", "numNonHornClauses", "maxNumAtomOcc", "numConstraints", "maxSizeNegBodyCon", "numAtomOccC"),"maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numConstraints + maxSizeNegBodyCon + numAtomOccC","spearman","\\#")
```

## maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numRules + maxSizeNegBodyCon
```{r spearman maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numRules + maxSizeNegBodyCon, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
genCors(c("maxSizeAnswerSet", "maxSizePosBodyNCon", "numNonHornClauses", "maxNumAtomOcc", "numRules", "maxSizeNegBodyCon"),"maxSizeAnswerSet + maxSizePosBodyNCon + numNonHornClauses + maxNumAtomOcc + numRules + maxSizeNegBodyCon","spearman","\\#")
```

# Number of High and Low Correlations per parameter
```{r Number of High Low Correlations per parameter, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
print(kable(paramHighLow[order(as.numeric(paramHighLow[, 2]), decreasing = TRUE), ], col.names = c("Parameter", "Times high", "Times low")))
```

```{r latexTables, echo=FALSE, message=FALSE, warning=FALSE,results='asis'}
timesLow <- timesLow[timesLow[,2]!=0,]
printTable(timesLow,"low")
printTable(timesHigh,"high")
timesNA <- timesNA[timesNA[,2]!=0,]
printTable(timesNA,"NA")
printTableHighLow()
numCorrelations
```
